%========================
% Jake's Clean Resume - Mohamed Fuad
% ATS-Optimized, Single Column, Tectonic-compatible
%========================
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{microtype}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Mohamed Fuad} \\ \vspace{3pt}
    \small
    +81 80-7535-2988 $|$
    \href{mailto:mohamed.fuad.jp@gmail.com}{\underline{mohamed.fuad.jp@gmail.com}} $|$
    \href{https://linkedin.com/in/mohamed-fuad-6b8483278}{\underline{linkedin.com/in/mohamed-fuad-6b8483278}} $|$
    \href{https://github.com/MohamedFuad16}{\underline{github.com/MohamedFuad16}}
\end{center}

\section{Summary}
\small{Third-year ICT student and full-stack developer focused on AI agent orchestration. I build multi-agent systems, LLM tool-calling, and secure MCP integrations across TypeScript, Python, Node, and AWS, and I work in both English and Japanese (JLPT N2).}
\vspace{3pt}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tokai University}{Tokyo, Japan}
      {Bachelor of Science in Information and Communication Technology}{Apr 2024 -- Mar 2028 (Expected)}
      \resumeItemListStart
        \resumeItem{3rd Year student, School of Information Science and Technology}
        \resumeItem{Relevant Coursework: Data Structures \& Algorithms, Computer Networks, Database Systems, Operating Systems, Software Engineering, Web Programming, Discrete Mathematics}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Translation Specialist}{Tokyo, Japan}
      {Altius Link (formerly KDDI Evolva)}{Jun 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Translate customer communications for users of KDDI services, supporting bilingual customer service.}
        \resumeItem{Apply precise wording, cultural nuance, and professional communication under real customer-facing conditions.}
      \resumeItemListEnd

    \resumeSubheading
      {Front Desk Associate}{Tokyo, Japan}
      {Hotel SUI Akasaka}{Apr 2023 -- Jul 2023}
      \resumeItemListStart
        \resumeItem{Handled guest inquiries, reservations, check-in support, and front-desk service in English and Japanese environments.}
      \resumeItemListEnd

    \resumeSubheading
      {Immigration Specialist at Haneda Airport}{Tokyo, Japan}
      {Japan Airlines}{Feb 2023 -- Apr 2023}
      \resumeItemListStart
        \resumeItem{Assisted document registration, web-verification workflows, and passenger guidance using English and Japanese.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{WebDrop} $|$ \emph{JavaScript, WebRTC, OPFS, Web Audio, Device Motion, Service Worker}}{2026}
          \resumeItemListStart
            \resumeItem{Building an AirDrop-style file sharing web app that runs entirely in the browser, with no native install and no manual device selection, using only built-in web platform APIs.}
            \resumeItem{Pairs nearby phones with a physical ``bump'' detected through the device motion sensor and an ultrasonic Web Audio handshake, then streams files peer-to-peer over WebRTC data channels with OPFS chunked storage.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Agent Swarm} $|$ \emph{Swift, SwiftUI, Python, Docker, AWS EC2, OpenAI Codex CLI, MCP}}{2026}
          \resumeItemListStart
            \resumeItem{Built a leader and agent orchestration runtime where a leader delegates work to parallel Codex agents in isolated Git worktrees, scaling up to 8 agents with a capacity planner that watches available CPU and RAM.}
            \resumeItem{Coordinated agents through a structured JSON task ledger with health monitoring and MCP-connected context sources, controlled from a macOS app with an iOS companion.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Tutor-System} $|$ \emph{TypeScript, React 19, OpenRouter, Deepgram, Dexie/IndexedDB, Express}}{2026}
          \resumeItemListStart
            \resumeItem{Built an AI learning app with function-calling tutor tools, a realtime voice tutor that splits foreground and background models, and source-aware chat grounded in the user's own PDFs.}
            \resumeItem{Engineered an auditable learner-memory layer with embeddings, semantic retrieval, and mastery tracking on an Express backend of around 6{,}000 lines.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{TokaiHub} $|$ \emph{TypeScript, React, Tailwind CSS, AWS Amplify, Cognito, Vite, PWA}}{2025}
          \resumeItemListStart
            \resumeItem{Developed a central student portal PWA for Tokai University with a mobile-first UI and bilingual support.}
            \resumeItem{Integrated custom AWS Cognito authentication and SES-backed OTP verification flows.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: TypeScript, JavaScript, Python, Swift, HTML/CSS, SQL, Java, C, Bash/Shell} \\
     \textbf{Frameworks \& Libraries}{: React, Node.js, Express, Flask, Tailwind CSS, SwiftUI, PWA, NumPy, Pandas} \\
     \textbf{Tools \& Databases}{: Git, GitHub, AWS (Amplify/Cognito/SES), Docker, SQLite, MySQL, VS Code, Vim} \\
     \textbf{AI \& Agents}{: Agent Orchestration, LLM Tool-Calling, MCP (Model Context Protocol), RAG / Semantic Retrieval, Codex \& OpenRouter} \\
     \textbf{Concepts}{: RESTful APIs, OOP, Design Patterns, Data Structures, WebRTC, Network Protocols, Agile} \\
     \textbf{Languages}{: English (Professional), Japanese (Business level, JLPT N2), Tamil (Native)}
    }}
 \end{itemize}

\end{document}
