%========================
% Awesome CV Modern Style — Mohamed Fuad
% Modern color accent, clean professional
% Tectonic-compatible (no fontawesome5)
%========================
\documentclass[10pt, a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{microtype}
\usepackage{setspace}

% --- COLOR PALETTE ---
\definecolor{accentblue}{RGB}{20, 60, 140}
\definecolor{darkgray}{RGB}{40, 40, 40}
\definecolor{medgray}{RGB}{90, 90, 90}
\definecolor{lightgray}{RGB}{220, 220, 220}

% --- PAGE GEOMETRY ---
\geometry{a4paper, top=0.8cm, bottom=0.8cm, left=1.2cm, right=1.2cm}

\hypersetup{hidelinks, colorlinks=true, urlcolor=accentblue}
\pagestyle{empty}
\setlength{\parindent}{0pt}

% --- SECTION STYLE ---
\titleformat{\section}
  {\color{accentblue}\normalsize\bfseries\scshape}
  {}{0em}{}
  [\vspace{-4pt}\color{accentblue}\rule{\linewidth}{1.2pt}\vspace{1pt}]
\titlespacing{\section}{0pt}{6pt}{3pt}

\newcommand{\cventry}[4]{%
  \vspace{1.5pt}
  \begin{tabularx}{\linewidth}{@{}Xr@{}}
    \textbf{\color{darkgray}#1} \textcolor{medgray}{\small $|$ #2} & \textcolor{medgray}{\small #4}\\
    \textcolor{accentblue}{\small\itshape #3} & \\
  \end{tabularx}
  \vspace{-1.5pt}
}

\newcommand{\cvproject}[3]{%
  \vspace{1.5pt}
  \begin{tabularx}{\linewidth}{@{}Xr@{}}
    \textbf{\color{darkgray}#1} \textcolor{medgray}{\small $|$ \textit{#2}} & \textcolor{medgray}{\small #3}\\
  \end{tabularx}
  \vspace{-1.5pt}
}

\newenvironment{cvbullets}{%
  \begin{itemize}[leftmargin=1em, itemsep=0.2pt, topsep=0.5pt, parsep=0pt]
  \small\color{darkgray}
}{%
  \end{itemize}\vspace{1pt}
}

\newcommand{\skillrow}[2]{%
  \textbf{\color{darkgray}\small #1:} & \small #2 \\[2pt]
}

\begin{document}

%=== HEADER ===
\begin{center}
  {\fontsize{22}{26}\selectfont \textbf{\color{accentblue}MOHAMED} \textbf{\color{darkgray}FUAD}}\\[3pt]
  {\small\color{medgray}\textit{Software Engineering Student --- ICT, Tokai University}}\\[4pt]
  {\small\color{medgray}
    Tel: 080-7535-2988 \quad $|$ \quad
    Email: \href{mailto:mohamed.fuad.jp@gmail.com}{mohamed.fuad.jp@gmail.com} \quad $|$ \quad
    Location: Setagaya, Tokyo, Japan
  }\\[2pt]
  {\small\color{medgray}
    LinkedIn: \href{https://linkedin.com/in/mohamed-fuad-6b8483278}{linkedin.com/in/mohamed-fuad-6b8483278} \quad $|$ \quad
    GitHub: \href{https://github.com/MohamedFuad16}{github.com/MohamedFuad16}
  }
\end{center}

\vspace{-2pt}
\color{accentblue}\rule{\linewidth}{1.5pt}
\vspace{1pt}

%=== PROFESSIONAL SUMMARY ===
\section{Professional Summary}
{\small\color{darkgray}
Highly motivated 3rd-year B.Sc. ICT student at Tokai University. Skilled in TypeScript, React, Node.js, and native Swift/macOS utilities. Builds practical AI-enabled learning tools and mobile PWA applications. Trilingual communicator (English, Japanese JLPT N2, Tamil) combining software engineering execution with precise communication.
}

%=== EDUCATION ===
\section{Education}
\cventry{Tokai University}{B.Sc. Information and Communication Technology}{School of Information Science \& Technology, Tokyo, Japan}{Apr 2024 -- Mar 2028}
\begin{cvbullets}
  \item 3rd Year in the ICT program, expected graduation March 2028
  \item Coursework: Algorithms \& Data Structures, Computer Networks, Database Systems, Operating Systems, Software Engineering, Web Programming, Discrete Mathematics
\end{cvbullets}

%=== EXPERIENCE ===
\section{Professional Experience}
\cventry{Altius Link (formerly KDDI Evolva)}{Translation Specialist}{Tokyo, Japan}{Jun 2023 -- Present}
\begin{cvbullets}
  \item Translate customer communications for users of KDDI services, supporting bilingual customer service.
  \item Apply precise wording, cultural nuance, and professional communication under real customer-facing conditions.
\end{cvbullets}

\cventry{Hotel SUI Akasaka}{Front Desk Associate}{Tokyo, Japan}{Apr 2023 -- Jul 2023}
\begin{cvbullets}
  \item Handled guest inquiries, reservations, check-in support, and front-desk service in English/Japanese environments.
\end{cvbullets}

\cventry{Japan Airlines}{Immigration Specialist at Haneda Airport}{Tokyo, Japan}{Feb 2023 -- Apr 2023}
\begin{cvbullets}
  \item Assisted document registration, web-verification workflows, and passenger guidance using English/Japanese.
\end{cvbullets}

%=== PROJECTS ===
\section{Projects}

\cvproject{Tutor-System $|$ \small\color{medgray}\href{https://github.com/MohamedFuad16/Tutor-System}{github.com/MohamedFuad16/Tutor-System}}{TypeScript, React 19, OpenRouter, Deepgram, Dexie/IndexedDB, Express}{2025}
\begin{cvbullets}
  \item Built an AI learning interface for PDF reading, source-aware tutor chat, voice tutoring, and concept revision.
\end{cvbullets}

\cvproject{TokaiHub $|$ \small\color{medgray}\href{https://github.com/MohamedFuad16/TokaiHub}{github.com/MohamedFuad16/TokaiHub}}{TypeScript, React, Tailwind CSS, AWS Amplify, Cognito, Vite, PWA}{2025}
\begin{cvbullets}
  \item Developed a central student portal PWA for Tokai University with mobile-first UI and bilingual support.
\end{cvbullets}

\cvproject{WebDrop $|$ \small\color{medgray}\href{https://github.com/MohamedFuad16/WebDrop}{github.com/MohamedFuad16/WebDrop}}{HTML, CSS, JavaScript, Node.js, WebRTC, OPFS, Service Worker}{2024 -- 2025}
\begin{cvbullets}
  \item Built a mobile-first nearby file-sharing app using WebRTC \texttt{RTCDataChannel} and OPFS chunked streaming.
\end{cvbullets}

\cvproject{Codex Account Switcher $|$ \small\color{medgray}\href{https://github.com/MohamedFuad16/Codex-Acc-Switcher}{github.com/MohamedFuad16/Codex-Acc-Switcher}}{Swift, AppKit, macOS Menu Bar, Process Control}{2025}
\begin{cvbullets}
  \item Created a native macOS menu-bar utility to switch active Codex profiles and hot-swap session tokens.
\end{cvbullets}

%=== TECHNICAL SKILLS ===
\section{Technical Skills}
\begin{tabular}{@{}p{0.20\linewidth}p{0.78\linewidth}@{}}
  \skillrow{Languages}{TypeScript, JavaScript, Python, Swift, HTML/CSS, SQL, Java, C, Bash/Shell}
  \skillrow{Frameworks}{React, Node.js, Express, Flask, Tailwind CSS, SwiftUI, PWA, NumPy, Pandas}
  \skillrow{Tools \& DevOps}{Git, GitHub, AWS (Amplify/Cognito/SES), Docker, SQLite, MySQL, VS Code, Vim}
  \skillrow{Concepts}{RESTful APIs, OOP, Design Patterns, Data Structures, WebRTC, Network Protocols, Agile}
  \skillrow{Languages}{English (Professional) $\cdot$ Japanese (Business, JLPT N2) $\cdot$ Tamil (Native)}
\end{tabular}

%=== ACTIVITIES ===
\section{Activities \& Interests}
\begin{itemize}[leftmargin=1em, itemsep=1pt, topsep=1pt]
  \item\small \textbf{IEEE Student Member} --- Tokai University Student Branch, participating in technical talks and seminars in the ICT field
  \item\small \textbf{Open Source Development} --- Actively maintaining GitHub repositories with consistent commit history and thorough documentation
\end{itemize}

\end{document}
