%========================
% Cover Letter for Mohamed Fuad
% HENNGE Global Internship Program
% Typography matched to Jake's Clean Resume (Tectonic-compatible)
%========================
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{microtype}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\begin{document}

\begin{center}
    {\Huge \scshape Mohamed Fuad} \\ \vspace{3pt}
    \small
    +81 80-7535-2988 $|$
    \href{mailto:mohamed.fuad.jp@gmail.com}{\underline{mohamed.fuad.jp@gmail.com}} $|$
    \href{https://linkedin.com/in/mohamed-fuad-6b8483278}{\underline{linkedin.com/in/mohamed-fuad-6b8483278}} $|$
    \href{https://github.com/MohamedFuad16}{\underline{github.com/MohamedFuad16}}
\end{center}

\vspace{10pt}
\hrule
\vspace{14pt}

\today

\vspace{8pt}

HENNGE K.K. \\
Hiring Team, Global Internship Program \\
Tokyo, Japan

\vspace{8pt}

Dear HENNGE Hiring Team,

My name is Mohamed Fuad, and I am a third-year Information and Communication Technology student at Tokai University in Tokyo, applying to HENNGE's Global Internship Program. I just finished your backend coding challenge in Python, and working through the recursion problem and the RFC 6238 TOTP authentication reminded me how much I enjoy building things that have to be both correct and secure. That is a big part of why HENNGE appeals to me.

Most of my free time over the past couple of years has gone into building full-stack projects. Right now I am working on WebDrop, an AirDrop-style file sharing app that runs entirely in the browser, with no native app and no manual device picking. Two nearby phones simply ``bump'' to pair, using the device motion sensor and an ultrasonic audio handshake, and then send files straight to each other over WebRTC. I really enjoy pushing the web platform to do things people usually assume need a native app.

I have also become fascinated by AI agent orchestration. I built Agent Swarm, where a ``leader'' delegates tasks to several Codex agents running in parallel inside isolated Git worktrees, with a capacity planner that scales up to eight agents and a task ledger that keeps them coordinated. In Tutor-System, a local-first AI study app, I added function-calling tutor tools, a realtime voice tutor, and an auditable learner-memory layer. To let these agents act on real systems safely, I wrote a FastAPI MCP server that connects AI clients to my university's Microsoft Teams workflows; it can read classes, assignments, and files and prepare drafts, but I deliberately built it so it can never submit anything on my behalf without my review. Designing that permission model is what got me thinking seriously about security, and about what an automated client should and should not be allowed to do. That is exactly why I want to intern at HENNGE, where cloud, email, and security all come together.

On the full-stack side I am comfortable across TypeScript and React, Node, Python, and AWS (Cognito, SES, and Amplify), and I work in both English and Japanese (JLPT N2), which I hope would help me contribute in HENNGE's bilingual environment. I would be grateful for the chance to learn from your engineers and to keep growing as a developer. Thank you very much for considering my application. My CV is attached, and I would be happy to walk through any of these projects in more detail.

\vspace{10pt}

Sincerely, \\
Mohamed Fuad

\end{document}
